Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
com nets

Varying social scales can have different fitness repercussions for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
but stronger and more stable social associates and grooming partners rather than
simply more associates [@Ellis_2019].  It is a common trope that individuals
must be associating to interact, and many studies assume that proximity is proxy
for interacting [@Farine_2015a]. For instance, baboons must be within proximity
of each other for grooming yet other animals use interactions that do not
require proximity such as long-distance vocalization or olfactory signals
[@Carter_2015]. It is possible to record social interactions that do not require
proximity using, for example, microphone arrays to construct long-distance
communication networks [@Snijders_2017]. Our results indicate varying social
patterns in different habitat types, potentially suggesting different types of
interactions. Higher graph strength in forage and open habitats may indicate
that caribou use visual or other cues not relevant in forest habitats (Figure
\@ref(fig:socres)).

>>>>

Varying social scales can have different fitness repercussions for individuals.
Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
but stronger and more stable social associates and grooming partners rather than
simply more associates [@Ellis_2019].  It is a common trope that individuals
must be associating to interact, and many studies assume that proximity is proxy
for interacting [@Farine_2015a]. For instance, baboons must be within proximity
of each other for grooming yet other animals interact using communication
such as long-distance vocalization or olfactory signals 
[@Carter_2015]. It is possible to record social interactions that do not require
proximity using, for example, microphone arrays to construct long-distance
communication networks [@Snijders_2017]. Our results indicate varying social
patterns in different habitat types, potentially suggesting different types of
interactions. Higher graph strength in forage and open habitats may indicate
that caribou use visual or other cues not relevant in forest habitats (Figure
\@ref(fig:socres)).
